---
title: "NovaSeq_Analysis"
author: "Tush"
date: "18/04/2019"
output:html_document
---

#pca-174 # 01/06/2020
```{r  }
library(ggplot2)
library(ggnewscale)
library(RColorBrewer)

egvec_174 <- read.delim(file.choose())
egval_174 <- read.delim(file.choose(), header = FALSE)
pdata <- read.csv(file.choose())

egvec_merge174 <- merge(pdata, egvec_174, by.x = "Sanger_Sample_ID", by.y ="IID")

sum_egval174<-sum(egval_174$V1)
sum_egval174<-lapply(egval_174$V1,function(x){
  rt<-(x/sum_egval174)*100
  rt<-round(rt)
  return(rt)
})

ggplot(egvec_merge174, aes((PC1),(PC2))) + geom_point(aes(color=as.factor(Time.point)), size=1) + theme_bw() + xlab(paste0("PC1 (",sum_egval174[[1]],"% total variance)")) + ylab(paste0("PC2 (",sum_egval174[[2]],"% total variance)")) + scale_color_discrete(name = "Time-point") + theme(plot.title = element_text(hjust = 0.5))

ggplot(egvec_merge174, aes((PC1),(PC2))) + geom_point(aes(color=as.factor(Treatment)), size=1) + theme_bw() + 
xlab(paste0("PC1 (",sum_egval174[[1]],"% total variance)")) + ylab(paste0("PC2 (",sum_egval174[[2]],"% total variance)")) + scale_color_discrete(name = "Treatment") + theme(plot.title = element_text(hjust = 0.5))

ggplot(egvec_merge174, aes((PC1),(PC2))) + geom_point(aes(color=as.factor(Island)), size=1) + theme_bw() + xlab(paste0("PC1 (",sum_egval174[[1]],"% total variance)")) + ylab(paste0("PC2 (",sum_egval174[[2]],"% total variance)")) + scale_color_discrete(name = "Treatment") + theme(plot.title = element_text(hjust = 0.5))
#************************************************************************#

egvec_merge174$PC2>0.6

ggplot(egvec_merge174, aes((PC3),(PC4))) + geom_point(aes(color=as.factor(Island)), size=1) + theme_bw() + 
xlab(paste0("PC3 (",sum_egval174[[3]],"% total variance)")) +
ylab(paste0("PC4 (",sum_egval174[[4]],"% total variance)")) + scale_color_discrete(name = "Location") + ggtitle("Population stratification by sample location") + theme(plot.title = element_text(hjust = 0.5))

ggplot(egvec_merge174, aes((PC5),(PC6))) + geom_point(aes(color=as.factor(Time.point)), size=1) + theme_bw() + 
xlab(paste0("PC5 (",sum_egval174[[5]],"% total variance)")) +
ylab(paste0("PC6 (",sum_egval174[[6]],"% total variance)")) + scale_color_discrete(name = "Treatment") + ggtitle("Population stratification by Time point") + theme(plot.title = element_text(hjust = 0.5))

ggplot(egvec_merge174, aes((PC7),(PC8))) + geom_point(aes(color=as.factor(Treatment))) + theme_bw() + 
xlab(paste0("PC7 (",sum_egval174[[7]],"% total variance)")) +
ylab(paste0("PC8 (",sum_egval174[[8]],"% total variance)")) + scale_color_discrete(name = "Treatment") + ggtitle("Population stratification by Treatment") + theme(plot.title = element_text(hjust = 0.5))

ggplot(egvec_merge174, aes((PC9),(PC10))) + geom_point(aes(color=as.factor(Time.point))) + theme_bw() + 
xlab(paste0("PC9 (",sum_egval174[[9]],"% total variance)")) +
ylab(paste0("PC10 (",sum_egval174[[10]],"% total variance)")) + scale_color_discrete(name = "Treatment") + ggtitle("Population stratification by time-point") + theme(plot.title = element_text(hjust = 0.5))
```

#pca_201 #01/06/2020
```{r }
library(ggnewscale)
library(RColorBrewer)
library(ggplot2)

egvec_201 <- read.delim(file.choose())
egval_201 <- read.delim(file.choose(), header = FALSE)
pdata_2 <- read.csv(file.choose())
egvec_merge201 <- merge(pdata_2, egvec_201, by.x = "Sanger_Sample_ID", by.y ="IID")

sum_egval201<-sum(egval_201$V1)
sum_egval201<-lapply(egval_201$V1,function(x){
  rt<-(x/sum_egval201)*100
  rt<-round(rt)
  return(rt)
})

#make a look-up table to get them in the right order
color_lookup <- setNames(c(brewer.pal(8,"Set1"),rep("grey80",3),"grey50"),c(as.character(unique(egvec_merge201$Vname[egvec_merge201$Location == "Island"])),as.character(unique(egvec_merge201$Vname[egvec_merge201$Location == "Shoreline"])),as.character(unique(egvec_merge201$Vname[egvec_merge201$Location == "Inland"]))))

VillageColors <- color_lookup[levels(egvec_merge201$Vname)]

ggplot(egvec_merge201, aes((PC1),(PC2))) + geom_point(aes(color=as.factor(Location)),size=3) + scale_color_manual(values=c("grey50","grey30","grey80"),name = "Group") + new_scale_color() + geom_point(aes(color=as.factor(Vname)),size=1.5) + scale_color_manual(values=VillageColors,name = "Village",limits= as.character(unique(egvec_merge201$Vname[egvec_merge201$Location == "Island"])) ) + theme_bw() +xlab(paste0("PC1 (",sum_egval201[[1]],"% total variance)")) +ylab(paste0("PC2 (",sum_egval201[[2]],"% total variance)")) +  theme(plot.title = element_text(hjust = 0.5))

ggplot(egvec_merge201, aes((PC1),(PC2))) + geom_point(aes(color=as.factor(Location)), size=1) + theme_bw() + 
xlab(paste0("PC1 (",sum_egval201[[1]],"% total variance)")) +
ylab(paste0("PC2 (",sum_egval201[[2]],"% total variance)")) + scale_color_discrete(name = "Location") + theme(plot.title = element_text(hjust = 0.5))

ggplot(egvec_merge201, aes((PC1),(PC2))) + geom_point(aes(color=as.factor(Vname)), size=1) + theme_bw() + 
xlab(paste0("PC1 (",sum_egval201[[1]],"% total variance)")) +
ylab(paste0("PC2 (",sum_egval201[[2]],"% total variance)")) + scale_color_discrete(name = "Vname") + theme(plot.title = element_text(hjust = 0.5))

dots9 <- egvec_201$PC2<-0.2
xx <- pdata %>% filter(Treatment=="Intensive", Tp == 2)

egvec_201$PC2< -0.2

ggplot(egvec_merge201, aes((PC3),(PC4))) + geom_point(aes(color=as.factor(Location)), size=1) + theme_bw() + 
xlab(paste0("PC3 (",sum_egval201[[3]],"% total variance)")) +
ylab(paste0("PC4 (",sum_egval201[[4]],"% total variance)")) + scale_color_discrete(name = "Location") + theme(plot.title = element_text(hjust = 0.5)) #+geom_point(aes(shape=Vname))

ggplot(egvec_merge201, aes((PC5),(PC6))) + geom_point(aes(color=as.factor(Location))) + theme_bw() + 
xlab(paste0("PC5 (",sum_egval201[[5]],"% total variance)")) +
ylab(paste0("PC6 (",sum_egval201[[6]],"% total variance)")) + scale_color_discrete(name = "Location") + ggtitle("Population stratification by Location") + theme(plot.title = element_text(hjust = 0.5))

ggplot(egvec_merge201, aes((PC7),(PC8))) + geom_point(aes(color=as.factor(Location))) + theme_bw() + 
xlab(paste0("PC7 (",sum_egval201[[7]],"% total variance)")) +
ylab(paste0("PC8 (",sum_egval201[[8]],"% total variance)")) + scale_color_discrete(name = "Location") + ggtitle("Population stratification by location") + theme(plot.title = element_text(hjust = 0.5))

ggplot(egvec_merge201, aes((PC9),(PC10))) + geom_point(aes(color=as.factor(Location))) + theme_bw() + 
xlab(paste0("PC9 (",sum_egval201[[9]],"% total variance)")) +
ylab(paste0("PC10 (",sum_egval201[[10]],"% total variance)")) + scale_color_discrete(name = "Location") + ggtitle("Population stratification by location") + theme(plot.title = element_text(hjust = 0.5))
```

#Fixation Index Test#
```{r }
fst_arm10kb <- read.table(file.choose(), header = T)
fst_tpt25kb <- read.table(file.choose(), header = T)
fst_Island10kb <- read.table(file.choose(), header = T)
fst_islands.outgrp10kb <- read.table(file.choose(), header = T)
fst_islands.shoreline10kb <- read.table(file.choose(), header = T)
fst_islands.inland10kb <- read.table(file.choose(), header = T)
fst_inland.shoreline10kb <- read.table(file.choose(), header = T)
pre10kb_std.int <- read.table(file.choose(), header = T)
post10kb_std.int <- read.table(file.choose(), header = T)
pre.post_10kb <- read.table(file.choose(), header = T)

pre.std_int.10kb <- subset(pre10kb_std.int, CHROM=="SM_V7_1" | CHROM=="SM_V7_ZW" | CHROM=="SM_V7_3" |  CHROM=="SM_V7_4" | CHROM=="SM_V7_5" | CHROM=="SM_V7_6" | CHROM=="SM_V7_7" | CHROM=="SM_V7_2")
pre.std_int.10kb$JV <- seq.int(nrow(pre.std_int.10kb))

post.std_int.10kb <- subset(post10kb_std.int, CHROM=="SM_V7_1" | CHROM=="SM_V7_2" | CHROM=="SM_V7_3" | CHROM=="SM_V7_4" | CHROM=="SM_V7_5" | CHROM=="SM_V7_6" | CHROM=="SM_V7_7" | CHROM=="SM_V7_ZW")

post.std_int.10kb$TJ <- seq.int(nrow(post.std_int.10kb))

post_pre.10kb <- subset(pre.post_10kb, CHROM=="SM_V7_1" | CHROM=="SM_V7_2" | CHROM=="SM_V7_3" | CHROM=="SM_V7_4" | CHROM=="SM_V7_5" | CHROM=="SM_V7_6" | CHROM=="SM_V7_7" | CHROM=="SM_V7_ZW")
#***************************************#pre

#assumes you have your data per window in a big vector called ALL_FST_VALUES
mean_FST_pre <- mean(pre.std_int.10kb$WEIGHTED_FST)
median_FST_pre <- median(pre.std_int.10kb$WEIGHTED_FST)
bstrap_means_pre <- c()
bstrap_medians_pre <- c()
for (i in 1:100) { 
 bstrap_medians_pre <- c(bstrap_medians_pre,median(sample(pre.std_int.10kb$WEIGHTED_FST,size=length(pre.std_int.10kb$WEIGHTED_FST),replace=TRUE)))
 bstrap_means_pre <- c(bstrap_means_pre,mean(sample(pre.std_int.10kb$WEIGHTED_FST,size=length(pre.std_int.10kb$WEIGHTED_FST),replace=TRUE)))
}
#these are symmetric 99% bootstrap confidence intervals for your median and mean, respectively
quantile(bstrap_medians_pre,c(0.005,0.995))
quantile(bstrap_means_pre,c(0.005,0.995))
#these are symmetric 95% bootstrap confidence intervals for your median and mean
quantile(bstrap_medians_pre,c(0.025,0.975))
quantile(bstrap_means_pre,c(0.025,0.975))

#***************************************#post
mean_FST_post <- mean(post.std_int.10kb$WEIGHTED_FST)
median_FST_post <- median(post.std_int.10kb$WEIGHTED_FST)
bstrap_means_post <- c()
bstrap_medians_post <- c()
for (i in 1:100) { 
 bstrap_medians_post <- c(bstrap_medians_post,median(sample(post.std_int.10kb$WEIGHTED_FST,size=length(post.std_int.10kb$WEIGHTED_FST),replace=TRUE)))
 bstrap_means_post <- c(bstrap_means_post,mean(sample(post.std_int.10kb$WEIGHTED_FST,size=length(post.std_int.10kb$WEIGHTED_FST),replace=TRUE)))
}
#these are symmetric 99% bootstrap confidence intervals for your median and mean, respectively
quantile(bstrap_medians_post,c(0.005,0.995))
quantile(bstrap_means_post,c(0.005,0.995))
#these are symmetric 95% bootstrap confidence intervals for your median and mean
quantile(bstrap_medians_post,c(0.025,0.975))
quantile(bstrap_means_post,c(0.025,0.975))
```

# bootstrap for trial
```{r}

fst_arm10kb <- subset(fst_arm10kb, CHROM=="SM_V7_1" | CHROM=="SM_V7_ZW" | CHROM=="SM_V7_3" |  CHROM=="SM_V7_4" | CHROM=="SM_V7_5" | CHROM=="SM_V7_6" | CHROM=="SM_V7_7" | CHROM=="SM_V7_2")
fst_arm10kb$JT <- seq.int(nrow(fst_arm10kb))

mean_FST_arm <- mean(fst_arm10kb$WEIGHTED_FST)
median_FST_arm <- median(fst_arm10kb$WEIGHTED_FST)
bstrap_means_arm <- c()
bstrap_medians_arm <- c()
for (i in 1:100) { 
 bstrap_medians_arm <- c(bstrap_medians_arm,median(sample(fst_arm10kb$WEIGHTED_FST,size=length(fst_arm10kb$WEIGHTED_FST),replace=TRUE)))
 bstrap_means_arm <- c(bstrap_means_arm,mean(sample(fst_arm10kb$WEIGHTED_FST,size=length(fst_arm10kb$WEIGHTED_FST),replace=TRUE)))
}
#these are symmetric 99% bootstrap confidence intervals for your median and mean, respectively
quantile(bstrap_medians_arm,c(0.005,0.995))
quantile(bstrap_means_arm,c(0.005,0.995))
#these are symmetric 95% bootstrap confidence intervals for your median and mean
quantile(bstrap_medians_arm,c(0.025,0.975))
quantile(bstrap_means_arm,c(0.025,0.975))

```

#bootstrap values for villages
```{r }
#assumes you have your data per window in a big vector called ALL_FST_VALUES
kakeeka.kachanga <- read.table(file.choose(), header = TRUE)
mean_kakeeka.kachanga <- mean(kakeeka.kachanga$WEIR_AND_COCKERHAM_FST, na.rm = TRUE)
median_kakeeka.kachanga <- median(kakeeka.kachanga$WEIR_AND_COCKERHAM_FST, na.rm = TRUE)
bstrap_means_kakeeka.kachanga <- c()
bstrap_medians_kakeeka.kachanga <- c()
for (i in 1:100) { 
 bstrap_medians_kakeeka.kachanga <- c(bstrap_medians_kakeeka.kachanga, median(sample(kakeeka.kachanga$WEIR_AND_COCKERHAM_FST,size=length(kakeeka.kachanga$WEIR_AND_COCKERHAM_FST),replace=TRUE), na.rm = TRUE))
 bstrap_means_kakeeka.kachanga <- c(bstrap_means_kakeeka.kachanga, mean(sample(kakeeka.kachanga$WEIR_AND_COCKERHAM_FST,size=length(kakeeka.kachanga$WEIR_AND_COCKERHAM_FST),replace=TRUE), na.rm = TRUE))
}
#these are symmetric 99% bootstrap confidence intervals for your median and mean, respectively
quantile(bstrap_medians_kakeeka.kachanga,c(0.005,0.995))
quantile(bstrap_means_kakeeka.kachanga,c(0.005,0.995))
```


```{r }
fst_islands.shoreline10kb_subset <- subset(fst_islands.shoreline10kb, CHROM=="SM_V7_4_5" | CHROM=="SM_V7_1_1" | CHROM=="SM_V7_2_4" | CHROM=="SM_V7_3_3" | CHROM=="SM_V7_5_6" | CHROM=="SM_V7_6_7" | CHROM=="SM_V7_7_8" | CHROM=="SM_V7_ZW_2")

fst_islands.inland10kb_subset <- subset(fst_islands.mainland10kb, CHROM=="SM_V7_4_5" | CHROM=="SM_V7_1_1" | CHROM=="SM_V7_2_4" | CHROM=="SM_V7_3_3" | CHROM=="SM_V7_5_6" | CHROM=="SM_V7_6_7" | CHROM=="SM_V7_7_8" | CHROM=="SM_V7_ZW_2")

fst_inland.shoreline10kb_subset <- subset(fst_inland.shoreline10kb, CHROM=="SM_V7_4_5" | CHROM=="SM_V7_1_1" | CHROM=="SM_V7_2_4" | CHROM=="SM_V7_3_3" | CHROM=="SM_V7_5_6" | CHROM=="SM_V7_6_7" | CHROM=="SM_V7_7_8" | CHROM=="SM_V7_ZW_2")

#windows vs number of snps#
ggscatter(pre25kb, x = "N_VARIANTS", y = "WEIGHTED_FST", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson", xlab = "Number of variants", ylab = "Weir and Cockerham weighted Fst", add = "reg.line", palette = c("blue", "green"), color = "blue", ellipse.level = 0.95, main = "Pearson correlation between fst and Number of varinats per 10kb window") + theme(plot.title = element_text(hjust = 0.5))

fst10kb_arm_subset_2 <- subset(fst10kb_arm_subset, N_VARIANTS>100)

### ploting each xsome individually with position where the variation occurs
ggplot(data = subset(fst, CHROM=="SM_V7_ZW"), aes(POS, WEIR_AND_COCKERHAM_FST)) + ggtitle("Fst for standard vs intensive trial arms, Chrom_ZW") + geom_point(na.rm = TRUE)

#back to plots for all chromosome#
xx <- pdata %>% filter(Treatment=="Intensive", Tp == 2)

ggplot(data = pre.std_int.10kb , aes(1:nrow(pre.std_int.10kb), WEIGHTED_FST,col=CHROM)) + geom_point(na.rm = TRUE, size=0.3) + ggtitle("Genetic differentiation between standard vs intensive among pre-treatment populations") + theme_bw() + theme(plot.title = element_text(hjust = 0.5)) + xlab("") + ylim(0,0.2) + xlab("Genomic windows (10kb)") + scale_color_discrete(name = "Chromosome")

ggplot(data = post.std_int.10kb, aes(1:nrow(post.std_int.10kb), WEIGHTED_FST,col=CHROM)) + geom_point(na.rm = TRUE, size=0.3) + ggtitle("Genetic differentiation between standard vs intensive among post-treatment populations") + theme(legend.position="none") + theme_bw() + theme(plot.title = element_text(hjust = 0.5)) + xlab("") + ylim(0,0.2) + scale_color_discrete(name = "Chromosome")

ggplot(data = post.std_int.10kb, aes(1:nrow(post.std_int.10kb), WEIGHTED_FST,col=CHROM)) + geom_rect(aes(xmin=9829,ymin=0.00,xmax=9844,ymax=0.20), fill="grey", color="grey") + geom_point(size=0.3) + ggtitle("Genetic differentiation between standard vs intensive among post-treatment populations") + theme(legend.position="none") + theme_bw() + theme(plot.title = element_text(hjust = 0.5)) + xlab("") 

ggplot(data = post.std_int.10kb, aes(1:nrow(post.std_int.10kb), WEIGHTED_FST,col=CHROM)) + geom_rect(aes(xmin=31211,ymin=0.00,xmax=31300,ymax=0.20), fill="grey", color="grey") + geom_point(size=0.3) + ggtitle("Genetic differentiation between standard vs intensive among post-treatment populations") + theme(legend.position="none") + theme_bw() + theme(plot.title = element_text(hjust = 0.5)) + xlab("")

xx <- post.std_int.10kb %>% filter(post.std_int.10kb$WEIGHTED_FST > 0.15) # quite useful

#*******************************************************
#Calculating bootstrap values.
#*******************************************************

post10kb$CHROM <- as.factor(post10kb$CHROM)

post <- ggplot(post10kb, aes(CHROM, WEIGHTED_FST, col=CHROM))  + geom_violin(trim = F) + theme_bw() + ggpubr::rotate_x_text()  + ggtitle("Genetic differentiation between standard(n=23) vs intensive(n=29) arms among post-treatment parasite populations") +theme(legend.position="none")  + theme(plot.title = element_text(hjust = 0.5)) + xlab(" Chromosomes (Genomic windows 10kb)") + stat_summary(fun=median, geom="point", size=1, color="blue") + ylim(-0.05 ,0.2)

pre <- ggplot(pre10kb, aes(CHROM, WEIGHTED_FST,col=CHROM)) + geom_violin(trim = F) + theme_bw() + ggpubr::rotate_x_text() + ggtitle("Genetic differentiation between standard(n=73) and intensive(n=49) arms among pre-treatment parasite populations") +theme(legend.position="none")  + theme(plot.title = element_text(hjust = 0.5)) + xlab("chromosomes (Genomic windows 10kb)")  + stat_summary(fun=median, geom="point", size=1, color="blue") + ylim(-0.05,0.2)

ggplot(data = pre10kb , aes(1:nrow(pre10kb), WEIGHTED_FST,col=CHROM)) + geom_point(na.rm = TRUE, size=0.3) + ggtitle("Genetic differentiation between standard(n=72) and intensive(n=50) among pre-treatment populations") +theme(legend.position="none") + theme_bw() + theme(plot.title = element_text(hjust = 0.5)) + xlab("") + ylim(0,0.2) + xlab("Genomic windows (10kb)")


ggplot(data = pre10kb , aes(1:nrow(pre10kb), WEIGHTED_FST,col=CHROM)) + geom_point(na.rm = TRUE, size=0.3) + ggtitle("Genetic differentiation between standard(n=72) and intensive(n=50) among pre-treatment populations") +theme(legend.position="none") + theme_bw() + theme(plot.title = element_text(hjust = 0.5)) + xlab("") + ylim(0,0.2) + xlab("Genomic windows (10kb)")

ggplot(data = fst_islands.shoreline10kb_subset, aes(1:nrow(fst_islands.shoreline10kb_subset), WEIGHTED_FST,col=CHROM)) + geom_point(na.rm = TRUE, size=0.3) + ggtitle("Fst between islands and shoreline")+theme(legend.position="none") + theme_bw() + theme(plot.title = element_text(hjust = 0.5)) + xlab("Genomic windows (10kb)") + ylim(0,1)

ggplot(data = fst_islands.inland10kb_subset, aes(1:nrow(fst_islands.inland10kb_subset), WEIGHTED_FST,col=CHROM)) + geom_point(na.rm = TRUE, size=0.3) + ggtitle("Fst between islands and inland")+theme(legend.position="none") + theme_bw() + theme(plot.title = element_text(hjust = 0.5)) + xlab("Genomic windows (10kb)") + ylim(0,1)

ggplot(data = fst_inland.shoreline10kb_subset, aes(1:nrow(fst_inland.shoreline10kb_subset), WEIGHTED_FST,col=CHROM)) + geom_point(na.rm = TRUE, size=0.3) + ggtitle("Fst between inland and shoreline")+theme(legend.position="none") + theme_bw() + theme(plot.title = element_text(hjust = 0.5)) + xlab("Genomic windows (10kb)") + ylim(0,1)
```

plotting Tajima's D statistics
```{r  }
tajima50kb <- read.table(file.choose(), header = T)
tajima10kb <- read.table(file.choose(), header = T)
tajima25kb <- read.table(file.choose(), header = T)

td50kb <- subset(tajima50kb,  CHROM=="SM_V7_1" | CHROM=="SM_V7_2" | CHROM=="SM_V7_3" | CHROM=="SM_V7_4" | CHROM=="SM_V7_5" | CHROM=="SM_V7_6" | CHROM=="SM_V7_7" | CHROM=="SM_V7_ZW")

td10kb <- subset(tajima10kb, CHROM=="SM_V7_1" | CHROM=="SM_V7_2" | CHROM=="SM_V7_3" | CHROM=="SM_V7_4" | CHROM=="SM_V7_5" | CHROM=="SM_V7_6" | CHROM=="SM_V7_7" | CHROM=="SM_V7_ZW")

td25kb <- subset(tajima25kb, CHROM=="SM_V7_1" | CHROM=="SM_V7_2" | CHROM=="SM_V7_3" | CHROM=="SM_V7_4" | CHROM=="SM_V7_5" | CHROM=="SM_V7_6" | CHROM=="SM_V7_7" | CHROM=="SM_V7_ZW")

ggplot(data = td50kb, aes(1:nrow(td50kb), TajimaD,col=CHROM)) + geom_point(na.rm = TRUE, size=0.1) + theme(legend.position="none") + xlab("Genomic windows (50kb)") + theme_bw() + ggtitle("Genome-wide Tajima's D") + theme(plot.title = element_text(hjust = 0.5)) + labs(colour = "Chromosome")

ggplot(data = tajima10kb_subset, aes(1:nrow(tajima10kb_subset), TajimaD,col=CHROM)) + geom_point(na.rm = TRUE, size=0.1) + theme(legend.position="none") + xlab("Genomic windows (10kb)") + theme_bw() + ggtitle("Genome-wide Tajima's D") + theme(plot.title = element_text(hjust = 0.5)) + labs(colour = "Chromosome")

ggplot(data = td25kb, aes(1:nrow(tajima25kb_subset), TajimaD,col=CHROM)) + geom_point(na.rm = TRUE, size=0.1) + theme(legend.position="none") + xlab("Genomic windows (25kb)") + theme_bw() + ggtitle("Genome-wide Tajima's D") + theme(plot.title = element_text(hjust = 0.5)) + labs(colour = "Chromosome")

tajima25kb_subset$JV <- seq.int(nrow(tajima25kb_subset))

ggplot(data = tajima25kb_subset, aes(JV, TajimaD,col=CHROM)) + theme(legend.position="none") + xlab("Genomic windows (25kb)") + theme_bw() + ggtitle("Genome-wide Tajima's D") + theme(plot.title = element_text(hjust = 0.5)) + labs(colour = "Chromosome") + geom_rect(aes(xmin=10774,ymin=-5,xmax=10852,ymax=5), fill="grey", color="grey") + geom_point(na.rm = TRUE, size=0.1) + geom_hline(aes(yintercept = -2), linetype = "dashed", colour = "grey")+ geom_hline(aes(yintercept = 2), linetype = "dashed", colour = "grey")

cutoff.tajima <- subset(tajima25kb_subset, TajimaD< -2.0)

XPEHH_cutoff_std.int <- subset(XPEHH_std.int_2, mean>2.0)

#xmin=2590 >> 40550000 (40.55 Mb)
#xmax=2650 >> 43550000 (43.55 Mb)

#Ploting region of interest on chr2#
tajima_50kb_Chr2 <- subset(tajima_50kb_, CHROM=="SM_V7_2")

ggplot(data = tajima_50kb_Chr2, aes(1:nrow(tajima_50kb_Chr2), TajimaD,col=CHROM)) + geom_point(na.rm = TRUE, size=0.1) + ggtitle("TajimaD for Chromosome two") + theme(legend.position="none") + xlab("Chr2_Genomic windows (50kb)")

ggplot(data = tajima_50kb_Chr2, aes(BIN_START, TajimaD,col=CHROM)) + theme(legend.position="CHROM") + geom_rect(aes(xmin=41000000,ymin=-5,xmax=43400000,ymax=4), fill="grey", color="grey") + geom_point(na.rm = TRUE, size=0.1, color= "#B97908") + xlab("Chr2_Genomic windows (50kb)") + theme_bw() + ggtitle("Tajima's D for Chr2_region of interest") + theme(plot.title = element_text(hjust = 0.5))

#*** rgb(185,121,8, maxColorValue = 255)#
```

#plotting fst among individual villages#
```{r }
setwd("/Users/jt24/Desktop/PopGen_paper/Fst")
fst_villages <- read.csv(file.choose())
fst_villages <- read.csv("fst4.csv", header=T, stringsAsFactors=FALSE, fileEncoding="latin1")

#plotting fst for villages with distance between the villages#
scaleFactor <- max(fst_villages$fst) / max(fst_villages$linear_distance_km)

ggplot(data = fst_villages, aes(x = reorder(Villages, fst), y=fst)) + geom_col(aes(fill=location)) + theme_bw() + ggpubr::rotate_x_text() + geom_line(aes(x=Villages, y=linear_distance_km * scaleFactor, group=1)) + scale_y_continuous(name="Weir and Cockerham weighted Fst", sec.axis=sec_axis(~./scaleFactor, name="Linear distance (km)")) + xlab("Villages ordered by fst")

ggplot(data = fst_villages, aes(x = reorder(Villages, fst), y=fst)) + geom_col(aes(fill=location)) + theme_bw() + ggpubr::rotate_x_text() + geom_line(aes(x=Villages, y=linear_distance_km * scaleFactor, group=1)) + scale_y_continuous(name="Weir and Cockerham weighted Fst", sec.axis=sec_axis(~./scaleFactor, name="Linear distance (km)")) + xlab("Villages ordered by fst")

#adding a smoothes line to the upper line plot over the fst plots#
ggplot(data = fst_villages, aes(x = reorder(Villages, fst), y=fst)) + geom_col(aes(fill=location)) + theme_bw() + ggpubr::rotate_x_text() + geom_smooth(aes(x=Villages, y=linear_distance_km * scaleFactor, group=1)) + scale_y_continuous(name="Weir and Cockerham weighted Fst", sec.axis=sec_axis(~./scaleFactor, name="Linear distance (km)")) + xlab("Villages ordered by fst")

#computing correlation between distance and fst#
ggscatter(fst_villages, x = "linear_distance_km", y = "fst", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson", xlab = "Linear distance between villages (km)", ylab = "Weir and Cockerham weighted Fst", add = "reg.line", palette = c("blue", "green"), color = "blue", ellipse.level = 0.95, main = "Pearson correlation between fst and linear distance between villages") + theme(plot.title = element_text(hjust = 0.5))

#ordering by distance#
ggplot(data = fst_villages, aes(x = reorder(Villages, linear_distance_km), y=fst)) + geom_col(aes(fill=location)) + theme_bw() + ggpubr::rotate_x_text() + geom_line(aes(x=Villages, y=linear_distance_km * scaleFactor, group=1)) + scale_y_continuous(name="Weir and Cockerham weighted Fst", sec.axis=sec_axis(~./scaleFactor, name="Linear distance (km)")) + xlab("Villages ordered by linear distance")

ggcorr(fst_villages)

fst_villages$linear_distance_km <- as.factor(fst_villages$linear_distance_km)
ggplot(fst_villages, aes(x=linear_distance_km, y=fst))  + geom_violin(trim = F) + ggpubr::rotate_x_text()
```

```{r }
pdata <- read.csv(file.choose(), header = T)

ggplot(data = pdata,aes(x = reorder(Sanger_Sample_ID, -genome.coverage),y =  genome.coverage)) + ggpubr::rotate_x_text() + geom_bar(stat = "identity") +ggtitle("Genome coverage per sample") + xlab("Samples") + ylab("Genome coverage per sample") + geom_hline(yintercept = mean(pdata$genome.coverage), color="blue")

ggplot(data = pdata,aes(x = reorder(Sanger_Sample_ID, -genome.coverage),y =  genome.coverage), face="bold") + geom_bar(stat = "identity") + xlab("Samples") + ylab("Genome coverage per sample") + geom_hline(yintercept = mean(pdata$genome.coverage), color="blue") + theme(axis.ticks = element_blank(), axis.text.x = element_blank())
```

```{r  }
map <- read.table(file.choose(), header = FALSE)

map_chrz <- subset(map, V1=="SM_V7_1_1" | V1=="SM_V7_2_4" | V1=="SM_V7_3_3" | V1=="SM_V7_4_5" | V1=="SM_V7_5_6" | V1=="SM_V7_6_7" | V1=="SM_V7_7_8" | V1=="SM_V7_ZW_2")

map_chr1 <- subset(map_chrz, V1=="SM_V7_1_1")
map_chr2 <- subset(map_chrz, V1=="SM_V7_2_4")
map_chr3 <- subset(map_chrz, V1=="SM_V7_3_3")
map_chr4 <- subset(map_chrz, V1=="SM_V7_4_5")
map_chr5 <- subset(map_chrz, V1=="SM_V7_5_6")
map_chr6 <- subset(map_chrz, V1=="SM_V7_6_7")
map_chr7 <- subset(map_chrz, V1=="SM_V7_7_8")
map_chrzw <- subset(map_chrz, V1=="SM_V7_ZW_2")

write.csv(map_chr1, file = "map_chr1.csv")
write.csv(map_chr2, file = "map_chr2.csv")
write.csv(map_chr3, file = "map_chr3.csv")
write.csv(map_chr4, file = "map_chr4.csv")
write.csv(map_chr5, file = "map_chr5.csv")
write.csv(map_chr6, file = "map_chr6.csv")
write.csv(map_chr7, file = "map_chr7.csv")
write.csv(map_chrzw, file = "map_chrzw.csv")
```

Making a genetic map for chromosomes
```{r  }
map_chr1 <- read.delim(file.choose(), header = FALSE)
Chr1_map <- subset(map_chr1, select = c(1,3,2))
Chr1_map[, 3 -(23979)]
Chr1_map$cm <- c(Chr1_map[,3]-23979)* 3.50881/1000000
Chr1_mp <- subset(Chr1_map, select = c(1,2,4,3))
write.table(Chr1_mp, file = "Chr1_mp.txt", row.names = FALSE, quote = FALSE, sep = "\t")

map_chr2 <- read.delim(file.choose(), header = T)
map_chr2$cm <- c(map_chr2[,2]-5047 )* 4.97524/1000000
Chr2_mp <- subset(map_chr2, select = c(1,3,4,2))
write.table(Chr2_mp, file = "Chr2_mp.txt", row.names = FALSE, quote = FALSE, sep = "\t")

map_chr3 <- read.table(file.choose(), header = TRUE)
map_chr3$cm <- c(map_chr3[,2]-19752 )* 3.23627/1000000
Chr3_mp <- subset(map_chr3, select = c(1,3,4,2))
write.table(Chr3_mp, file = "Chr3_mp.txt", row.names = FALSE, quote = FALSE, sep = "\t")

map_chr4 <- read.delim(file.choose(), header = TRUE)
map_chr4$cm <- c(map_chr4[,2]-820)* 4.10342/1000000
Chr4_mp <- subset(map_chr4, select = c(1,3,4,2))
write.table(Chr4_mp, file = "Chr4_mp.txt", row.names = FALSE, quote = FALSE, sep = "\t")

map_chr5 <- read.delim(file.choose(), header = TRUE)
map_chr5$cm <- c(map_chr5[,2]-6547)* 3.90968/1000000
Chr5_mp <- subset(map_chr5, select = c(1,3,4,2))
write.table(Chr5_mp, file = "Chr5_mp.txt", row.names = FALSE, quote = FALSE, sep = "\t")

map_chr6 <- read.delim(file.choose(), header = TRUE)
map_chr6$cm <- c(map_chr6[,2]-50890)* 4.62264/1000000
Chr6_mp <- subset(map_chr6, select = c(1,3,4,2))
write.table(Chr6_mp, file = "Chr6_mp.txt", row.names = FALSE, quote = FALSE, sep = "\t")

map_chr7 <- read.delim(file.choose(), header = TRUE)
map_chr7$cm <- c(map_chr7[,2]-2518)* 5.97870/1000000
Chr7_mp <- subset(map_chr7, select = c(1,3,4,2))
write.table(Chr7_mp, file = "Chr7_mp.txt", row.names = FALSE, quote = FALSE, sep = "\t")

map_chrZW <- read.delim(file.choose(), header = TRUE)
map_chrZW$cm <- c(map_chrZW[,2]-1395)* 4.03130/1000000
ChrZW_mp <- subset(map_chrZW, select = c(1,3,4,2))
write.table(ChrZW_mp, file = "ChrZW_mp.txt", row.names = FALSE, quote = FALSE, sep = "\t")
```

#Annotation of iHS data tables*Standard#
```{r }
Chr1_std <- read.table(file.choose(), header = T)
Chr1_std$CHROM <- c("chr1")

Chr2_std <- read.table(file.choose(), header = T)
Chr2_std$CHROM <- c("chr2")

Chr3_std <- read.table(file.choose(), header = T)
Chr3_std$CHROM <- c("chr3")

Chr4_std <- read.table(file.choose(), header = T)
Chr4_std$CHROM <- c("chr4")

Chr5_std <- read.table(file.choose(), header = T)
Chr5_std$CHROM <- c("chr5")

Chr6_std <- read.table(file.choose(), header = T)
Chr6_std$CHROM <- c("chr6")

Chr7_std <- read.table(file.choose(), header = T)
Chr7_std$CHROM <- c("chr7")

Chrzw_std <- read.table(file.choose(), header = T)
Chrzw_std$CHROM <- c("chrZW")
```

#Annotation of iHS data tables*Intensive#
```{r  }
Chr1_int <- read.table(file.choose(), header = T)
Chr1_int$CHROM <- c("chr1")

Chr2_int <- read.table(file.choose(), header = T)
Chr2_int$CHROM <- c("chr2")

Chr3_int <- read.table(file.choose(), header = T)
Chr3_int$CHROM <- c("chr3")

Chr4_int <- read.table(file.choose(), header = T)
Chr4_int$CHROM <- c("chr4")

Chr5_int <- read.table(file.choose(), header = T)
Chr5_int$CHROM <- c("chr5")

Chr6_int <- read.table(file.choose(), header = T)
Chr6_int$CHROM <- c("chr6")

Chr7_int <- read.table(file.choose(), header = T)
Chr7_int$CHROM <- c("chr7")

Chrzw_int <- read.table(file.choose(), header = T)
Chrzw_int$CHROM <- c("chrZW")
#*************************************#
Chr1_int$start <- Chr1_int$Pos
Chr1_int$end <- Chr1_int$start

Chr2_int$start <- Chr2_int$Pos
Chr2_int$end <- Chr2_int$start

Chr3_int$start <- Chr3_int$Pos
Chr3_int$end <- Chr3_int$start

Chr4_int$start <- Chr4_int$Pos
Chr4_int$end <- Chr4_int$start

Chr5_int$start <- Chr5_int$Pos
Chr5_int$end <- Chr5_int$start

Chr6_int$start <- Chr6_int$Pos
Chr6_int$end <- Chr6_int$start

Chr7_int$start <- Chr7_int$Pos
Chr7_int$end <- Chr7_int$start

Chrzw_int$start <- Chrzw_int$Pos
Chrzw_int$end <- Chrzw_int$start
```

#adding a column "chr*" to respective files* ihs tp1#
```{R  }
Chr1_tp1 <- read.table(file.choose(), header = T)
Chr1_tp1$CHROM <- c("chr1")

Chr2_tp1 <- read.table(file.choose(), header = T)
Chr2_tp1$CHROM <- c("chr2")

Chr3_tp1 <- read.table(file.choose(), header = T)
Chr3_tp1$CHROM <- c("chr3")

Chr4_tp1 <- read.table(file.choose(), header = T)
Chr4_tp1$CHROM <- c("chr4")

Chr5_tp1 <- read.table(file.choose(), header = T)
Chr5_tp1$CHROM <- c("chr5")

Chr6_tp1 <- read.table(file.choose(), header = T)
Chr6_tp1$CHROM <- c("chr6")

Chr7_tp1 <- read.table(file.choose(), header = T)
Chr7_tp1$CHROM <- c("chr7")

Chrzw_tp1 <- read.table(file.choose(), header = T)
Chrzw_tp1$CHROM <- c("chrZW")
#*************************************#
Chr1_tp1$start <- Chr1_tp1$Pos
Chr1_tp1$end <- Chr1_tp1$start

Chr2_tp1$start <- Chr2_tp1$Pos
Chr2_tp1$end <- Chr2_tp1$start

Chr3_tp1$start <- Chr3_tp1$Pos
Chr3_tp1$end <- Chr3_tp1$start

Chr4_tp1$start <- Chr4_tp1$Pos
Chr4_tp1$end <- Chr4_tp1$start

Chr5_tp1$start <- Chr5_tp1$Pos
Chr5_tp1$end <- Chr5_tp1$start

Chr6_tp1$start <- Chr6_tp1$Pos
Chr6_tp1$end <- Chr6_tp1$start

Chr7_tp1$start <- Chr7_tp1$Pos
Chr7_tp1$end <- Chr7_tp1$start

Chrzw_tp1$start <- Chrzw_tp1$Pos
Chrzw_tp1$end <- Chrzw_tp1$start
```

#iHS tp2#
```{r  }
Chr1_tp2 <- read.table(file.choose(), header = T)
Chr1_tp2$CHROM <- c("chr1")

Chr2_tp2 <- read.table(file.choose(), header = T)
Chr2_tp2$CHROM <- c("chr2")

Chr3_tp2 <- read.table(file.choose(), header = T)
Chr3_tp2$CHROM <- c("chr3")

Chr4_tp2 <- read.table(file.choose(), header = T)
Chr4_tp2$CHROM <- c("chr4")

Chr5_tp2 <- read.table(file.choose(), header = T)
Chr5_tp2$CHROM <- c("chr5")

Chr6_tp2 <- read.table(file.choose(), header = T)
Chr6_tp2$CHROM <- c("chr6")

Chr7_tp2 <- read.table(file.choose(), header = T)
Chr7_tp2$CHROM <- c("chr7")

Chrzw_tp2 <- read.table(file.choose(), header = T)
Chrzw_tp2$CHROM <- c("chrZW")
#*******************************************#
Chr1_tp2$start <- Chr1_tp2$Pos
Chr1_tp2$end <- Chr1_tp2$start

Chr2_tp2$start <- Chr2_tp2$Pos
Chr2_tp2$end <- Chr2_tp2$start

Chr3_tp2$start <- Chr3_tp2$Pos
Chr3_tp2$end <- Chr3_tp2$start

Chr4_tp2$start <- Chr4_tp2$Pos
Chr4_tp2$end <- Chr4_tp2$start

Chr5_tp2$start <- Chr5_tp2$Pos
Chr5_tp2$end <- Chr5_tp2$start

Chr6_tp2$start <- Chr6_tp2$Pos
Chr6_tp2$end <- Chr6_tp2$start

Chr7_tp2$start <- Chr7_tp2$Pos
Chr7_tp2$end <- Chr7_tp2$start

Chrzw_tp2$start <- Chrzw_tp2$Pos
Chrzw_tp2$end <- Chrzw_tp2$start
```

#adding windows to iHS plots#
```{r }
Chr1_std$start <- Chr1_std$Pos
Chr1_std$end <- Chr1_std$start

Chr2_std$start <- Chr2_std$Pos
Chr2_std$end <- Chr2_std$start

Chr3_std$start <- Chr3_std$Pos
Chr3_std$end <- Chr3_std$start

Chr4_std$start <- Chr4_std$Pos
Chr4_std$end <- Chr4_std$start

Chr5_std$start <- Chr5_std$Pos
Chr5_std$end <- Chr5_std$start

Chr6_std$start <- Chr6_std$Pos
Chr6_std$end <- Chr6_std$start

Chr7_std$start <- Chr7_std$Pos
Chr7_std$end <- Chr7_std$start

Chrzw_std$start <- Chrzw_std$Pos
Chrzw_std$end <- Chrzw_std$start
```

#Combining chromosomes for iHS *and plotting the results*#
```{r}
library(rehh)

#iHS standard*Chr1_std, Chr2_std, Chr3_std, Chr4_std, Chr5_std, Chr6_std, Chr7_std, Chrzw_std#
Std_iHS <- rbind(Chr1_std, Chr2_std, Chr3_std, Chr4_std, Chr5_std, Chr6_std, Chr7_std, Chrzw_std)

bin <- 25000
STD_iHS <- Std_iHS %>% mutate(window = start %/% bin) %>% group_by(window, CHROM) %>% summarise(mean = mean(norm)) %>% mutate(start = (window*bin)+1, stop = (window+1)*bin)

STD_iHS_2 <- STD_iHS[order(STD_iHS$CHROM, STD_iHS$start),]
STD_iHS_2$XX <- seq.int(nrow(STD_iHS_2))

ggplot(data = STD_iHS_2, aes(XX, mean, color=as.factor(CHROM), group=CHROM)) + geom_point(size=0.1) + xlab("Genomic windows (25kb)") + ylab("iHS_standard") + theme_bw() + ylim(-4, 4) + scale_color_discrete(name = "Chromosome")

#plotting genome-wide distribution#
distribplot(STD_iHS_2$mean, xlab = "iHS_standard")

#adding one or 2 y intercepts#
ggplot(data = STD_iHS_2, aes(XX, mean, color=as.factor(CHROM), group=CHROM)) + geom_point(size=0.1) + xlab("Genomic windows (25kb)") + ylab("iHS_standard") + theme_bw() + ylim(-4, 4) + geom_hline(yintercept = -2) + geom_hline(yintercept = 2) + scale_color_discrete(name = "Chromosome")

ggplot(data = STD_iHS_2, aes(XX, mean, color=CHROM, group=CHROM)) + geom_point(size=0.1) + xlab("Genomic windows (25kb)") + ylab("iHS_standard") + theme_bw() + ylim(-4, 4) + geom_hline(aes(yintercept = -2), linetype = "dashed", colour = "grey") + labs(colour = "Chromosome") + geom_hline(aes(yintercept = 2), linetype = "dashed", colour = "grey")

ggplot(data = STD_iHS, aes(start, mean, color=as.factor(CHROM))) + geom_point(size=0.1) + xlab("Genomic windows (25kb)") + ylab("iHS_standard") + facet_grid(CHROM~.) + theme_bw()

ggplot(data = STD_iHS, aes(start, mean)) + geom_point(size=0.1) + xlab("Binstart_25kb") + ylab("iHS_standard") + facet_grid(cols = vars(CHROM)) + theme_bw()

ggplot(data = STD_iHS, aes(start, mean, color = as.factor(CHROM))) + geom_point(size=0.1) + xlab("Chromosomes") + ylab("iHS_standard") + scale_color_manual(values=c("red","blue","green","purple","orange","grey","yellow", "chocolate", "black","pink"))

#iHS intensive* Chr1_int, Chr2_int, Chr3_int, Chr4_int, Chr5_int, Chr6_int, Chr7_int, Chrzw_int#
Int_iHS <- rbind(Chr1_int, Chr2_int, Chr3_int, Chr4_int, Chr5_int, Chr6_int, Chr7_int, Chrzw_int)
bin <- 25000
INT_iHS <- Int_iHS %>% mutate(window = start %/% bin) %>% group_by(window, CHROM) %>% summarise(mean = mean(norm)) %>% mutate(start = (window*bin)+1, stop = (window+1)*bin)

INT_iHS_2 <- INT_iHS[order(INT_iHS$CHROM, INT_iHS$start),] 

INT_iHS_2$JV <- seq.int(nrow(INT_iHS_2))

ggplot(data = INT_iHS_2, aes(JV, mean, color=as.factor(CHROM))) + geom_point(size=0.1) + xlab("Binstart_25kb") + ylab("iHS_intensive") + theme_bw() + geom_rect(aes(xmin=4700,ymin=-4,xmax=4720,ymax=4, size =0.3), fill="grey", color="grey") + geom_point(na.rm = TRUE, size=0.1)

ggplot(data = INT_iHS_2, aes(JV, mean, color=as.factor(CHROM))) + geom_point(size=0.1) + xlab("Binstart_25kb") + ylab("iHS_intensive") + theme_bw() + geom_rect(aes(xmin=4700,ymin=-4,xmax=4720,ymax=4, size =0.3), fill="grey", color="grey") + geom_point(na.rm = TRUE, size=0.1)

ggplot(data = INT_iHS_2, aes(JV, mean, color=as.factor(CHROM))) + geom_point(size=0.1) + xlab("Genomic windows (25kb)") + ylab("iHS_intensive") + theme_bw() + geom_point(na.rm = TRUE, size=0.1) + ylim(-4, 4) + geom_hline(aes(yintercept = -2), linetype="dashed", colour="grey") + geom_hline(aes(yintercept = 2), linetype="dashed", colour="grey") + labs(colour = "Chromosome")

ggplot(data = INT_iHS_2, aes(JV, mean, color=as.factor(CHROM), group=CHROM)) + geom_point(size=0.1) + xlab("Binstart_25kb") + ylab("iHS_intensive") + theme_bw() + ylim(-4, 4)

distribplot(INT_iHS_2$mean, xlab = "iHS_intensive")

#plotting ihs.std vs iHS.int and coloring by chrom#
write.csv(STD_iHS_2, file = "std_ihs.csv")
write.csv(INT_iHS_2, file = "int_ihs.csv")

std.int_ihs <- read.csv(file.choose())

ggplot(data = na.omit(std.int_ihs), aes(x = mean_std, y = mean_int, color=as.factor(CHROM_int))) + theme_bw() + geom_point(na.rm = TRUE, size=0.1) + xlab('iHS_satndard') + ylab('iHS_intensive') + ggtitle("iHS_standard vs iHS_intensive and coloring by chromosome") + theme(plot.title = element_text(hjust = 0.5))

#iHS tp1 * Chr1_tp1, Chr2_tp1, Chr3_tp1, Chr4_tp1, Chr5_tp1, Chr6_tp1, Chr7_tp1, Chrzw_tp1#
TP1_iHS <- rbind(Chr1_tp1, Chr2_tp1, Chr3_tp1, Chr4_tp1, Chr5_tp1, Chr6_tp1, Chr7_tp1, Chrzw_tp1)
bin <- 25000
TP1_iHS <- TP1_iHS %>% mutate(window = start %/% bin) %>% group_by(window, CHROM) %>% summarise(mean = mean(norm)) %>% mutate(start = (window*bin)+1, stop = (window+1)*bin)

TP1_iHS_2 <- TP1_iHS[order(TP1_iHS$CHROM, TP1_iHS$start),]
TP1_iHS_2$TJ <- seq.int(nrow(TP1_iHS_2))

ggplot(data = TP1_iHS_2, aes(TJ, mean, color=as.factor(CHROM))) + geom_point(size=0.1) + xlab("Binstart_25kb") + ylab("iHS_pre-treatment") + theme_bw()  + geom_rect(aes(xmin=4700,ymin=-4,xmax=4720,ymax=4, size =0.3), fill="grey", color="grey") + geom_point(na.rm = TRUE, size=0.1)

distribplot(TP1_iHS_2$mean, xlab = "iHS_pre treatment")

ggplot(data = TP1_iHS_2, aes(TJ, mean, color=as.factor(CHROM))) + geom_point(size=0.1) + xlab("Genomic windows (25kb)") + ylab("iHS_pre-treatment") + theme_bw() + geom_point(na.rm = TRUE, size=0.1) + ylim(-4, 4) + geom_hline(yintercept = -2, color="grey", linetype="dashed") + geom_hline(yintercept = 2, color="grey", linetype="dashed") + labs(colour = "Chromosome")

# iHS tp2* Chr1_tp2, Chr2_tp2, Chr3_tp2, Chr4_tp2, Chr5_tp2, Chr6_tp2, Chr7_tp2, Chrzw_tp2#
TP2_iHS <- rbind(Chr1_tp2, Chr2_tp2, Chr3_tp2, Chr4_tp2, Chr5_tp2, Chr6_tp2, Chr7_tp2, Chrzw_tp2)
bin <- 25000
TP2_iHS <- TP2_iHS %>% mutate(window = start %/% bin) %>% group_by(window, CHROM) %>% summarise(mean = mean(norm)) %>% mutate(start = (window*bin)+1, stop = (window+1)*bin)

TP2_iHS_2 <- TP2_iHS[order(TP2_iHS$CHROM, TP2_iHS$start),]
TP2_iHS_2$VJ <- seq.int(nrow(TP2_iHS_2))

ggplot(data = TP2_iHS_2, aes(VJ, mean, color=as.factor(CHROM))) + geom_point(size=0.1) + xlab("Binstart_25kb") + ylab("iHS_post-treatment") + theme_bw() + geom_rect(aes(xmin=4700,ymin=-4,xmax=4720,ymax=4, size =0.3), fill="grey", color="grey") + geom_point(na.rm = TRUE, size=0.1)

distribplot(TP2_iHS_2$mean, xlab = "iHS_post treatment")

ggplot(data = TP2_iHS_2, aes(VJ, mean, color=as.factor(CHROM))) + xlab("Genomic windows (25kb)") + ylab("iHS_post-treatment") + theme_bw() + geom_point(na.rm = TRUE, size=0.1) + geom_hline(yintercept = -2, color="grey", linetype="dashed") + geom_hline(yintercept = 2, color="grey", linetype="dashed") + labs(colour = "Chromosome") + ylim(-4, 4)

#picking region on chr2#
TP2_iHS_2_Chr2 <- subset(TP2_iHS_2, CHROM=="chr2")

ggplot(data = TP2_iHS_2_Chr2, aes(VJ, mean, color=as.factor(CHROM))) + xlab("Chr2_Binstart_25kb") + ylab("iHS_post-treatment") + theme_bw() + geom_rect(aes(xmin=4700,ymin=-4,xmax=4720,ymax=4, alpha=0.2, size = 0.5), fill="grey", color="grey") + geom_point(na.rm = TRUE, size=0.1, color = "#B97908")

#plotting tp1 vs tp2 ihs & coloring by chromosome#
write.csv(TP1_iHS_2, file = "ihs_tp1.csv")
write.csv(TP2_iHS_2, file = "ihs_tp2.csv")

iHS_tp1.tp2 <- read.csv(file.choose())

ggplot(data = na.omit(iHS_tp1.tp2), aes(x = mean_tp1, y = mean_tp2, color=as.factor(CHROM_tp1))) + theme_bw() + geom_point(na.rm = TRUE, size=0.1) + xlab('iHS_pre-treatment') + ylab('iHS_post-treatment') + ggtitle("iHS_pre vs iHS_post treatment, coloring by chromosome") + theme(plot.title = element_text(hjust = 0.5))
```

#Reading-in xpehh#
```{r }
Chr1_Std.Int <- read.table(file.choose(), header = TRUE)
Chr2_Std.int <- read.table(file.choose(), header = TRUE)
Chr3_Std.int <- read.table(file.choose(), header = TRUE)
Chr4_std.int <- read.table(file.choose(), header = TRUE)
Chr5_std.int <- read.table(file.choose(), header = TRUE)
Chr6_std.int <- read.table(file.choose(), header = TRUE)
Chr7_std.int <- read.table(file.choose(), header = TRUE)
Chrzw_std.int <- read.table(file.choose(), header = TRUE)
```

#Combining chromosomes for XP-EHH and plotting the results#
```{r }
#XP-EHH std_int#
# Chr1_Std.Int, Chr2_Std.int, Chr3_Std.int, Chr4_std.int, Chr5_std.int, Chr6_std.int, Chr7_std.int, Chrzw_std.int#
# adding a chr* column in the dataset

Chr1_Std.Int$CHROM <- c("chr1")
Chr2_Std.int$CHROM <- c("chr2")
Chr3_Std.int$CHROM <- c("chr3")
Chr4_std.int$CHROM <- c("chr4")
Chr5_std.int$CHROM <- c("chr5")
Chr6_std.int$CHROM <- c("chr6")
Chr7_std.int$CHROM <- c("chr7")
Chrzw_std.int$CHROM <- c("chrZW")

Chr1_Std.Int$start <- Chr1_Std.Int$pos
Chr1_Std.Int$end <- Chr1_Std.Int$start

Chr2_Std.int$start <- Chr2_Std.int$pos
Chr2_Std.int$end <- Chr2_Std.int$start

Chr3_Std.int$start <- Chr3_Std.int$pos
Chr3_Std.int$end <- Chr3_Std.int$start

Chr4_std.int$start <- Chr4_std.int$pos
Chr4_std.int$end <- Chr4_std.int$start

Chr5_std.int$start <- Chr5_std.int$pos
Chr5_std.int$end <- Chr5_std.int$start

Chr6_std.int$start <- Chr6_std.int$pos
Chr6_std.int$end <- Chr6_std.int$start

Chr7_std.int$start <- Chr7_std.int$pos
Chr7_std.int$end <- Chr7_std.int$start

Chrzw_std.int$start <- Chrzw_std.int$pos
Chrzw_std.int$end <- Chrzw_std.int$start

XPEHH_std.int <- rbind(Chr1_Std.Int, Chr2_Std.int, Chr3_Std.int, Chr4_std.int, Chr5_std.int, Chr6_std.int, Chr7_std.int, Chrzw_std.int)

bin <- 25000
XPEHH_std.int <- XPEHH_std.int %>% mutate(window = start %/% bin) %>% group_by(window, CHROM) %>% summarise(mean = mean(normxpehh)) %>% mutate(start = (window*bin)+1, stop = (window+1)*bin)

XPEHH_std.int_2 <- XPEHH_std.int[order(XPEHH_std.int$CHROM, XPEHH_std.int$start),]

XPEHH_std.int_2$TV <- seq.int(nrow(XPEHH_std.int_2))

subset(XPEHH_std.int_2, XPEHH_std.int_2$mean > 2) -> selected.std
subset(XPEHH_std.int_2, XPEHH_std.int_2$mean < -2) -> selected.int
subset(XPEHH_std.int_2, XPEHH_std.int_2$mean < -2 | XPEHH_std.int_2$mean > 2) -> selected_std.int

ggplot(data = XPEHH_std.int_2, aes(TV, mean, color=as.factor(CHROM))) + geom_point(size=0.1) + xlab("Genomic windows (25kb)") + ylab("XPEHH_std.int") + theme_bw() + geom_rect(aes(xmin=12711,ymin=-5,xmax=12717,ymax=5), fill="grey", color="grey") + geom_point(na.rm = TRUE, size=0.1) + geom_hline(yintercept = -2, color="grey", linetype="dashed") + geom_hline(yintercept = 2, color="grey", linetype="dashed")

ggplot(data = XPEHH_std.int_2, aes(TV, mean, color=as.factor(CHROM))) + xlab("") + ylab("XPEHH_std.int") + theme_bw() + geom_point(na.rm = TRUE, size=0.1) + geom_hline(yintercept = -2, color="grey", linetype="dashed") + geom_hline(yintercept = 2, color="grey", linetype="dashed") + labs(colour = "Chromosome") + ylim(-5, 5)

XPEHH_cutoff_std.int <- subset(XPEHH_std.int_2, mean>2.0)
XPEHH_cutoff2_std.int <- subset(XPEHH_std.int_2, mean< -2.0)
distribplot(XPEHH_std.int_2$mean, xlab = "XP-EHH_std.int")
distribplot(XPEHH_tp1.tp2_2$mean, xlab = "XP-EHH_tp1.tp2")

#picking chrZW#
XPEHH_std.int_2_ChrZW <- subset(XPEHH_std.int_2, CHROM=="chrzw")

ggplot(data = XPEHH_std.int_2_ChrZW, aes(TV, mean, color=as.factor(CHROM))) + xlab("ChrZW_Binstart_25kb") + ylab("XPEHH_std.int_chrZW") + theme_bw() + geom_rect(aes(xmin=12000,ymin=-4,xmax=12020,ymax=4), fill="grey", color="grey") + geom_point(na.rm = TRUE, size=0.1)

#picking all regions >2 cutoff#
ggplot(data = XPEHH_std.int_2, aes(TV, mean, color=as.factor(CHROM))) + xlab("Genomic windows (25kb)") + ylab("XPEHH_std.int") + theme_bw() + geom_rect(aes(xmin=1070,ymin=-4,xmax=1081,ymax=4), fill="grey", color="grey") + geom_point(na.rm = TRUE, size=0.1) + geom_hline(yintercept = -2, color="purple") + geom_hline(yintercept = 2, color="purple") + labs(colour = "Chromosome")

ggplot(data = XPEHH_std.int_2, aes(TV, mean, color=as.factor(CHROM))) + xlab("Genomic windows (25kb)") + ylab("XPEHH_std.int") + theme_bw() + geom_rect(aes(xmin=13208,ymin=-4,xmax=13213,ymax=4), fill="grey", color="grey") + geom_point(na.rm = TRUE, size=0.1) + geom_hline(yintercept = -2, color="grey", linetype="dashed") + geom_hline(yintercept = 2, color="grey", linetype="dashed") + labs(colour = "Chromosome")

#XP-EHH pre and post treatment#
#Chr1_tp1.tp2, Chr2_tp1.tp2, Chr3_tp1.tp2, Chr4_tp1.tp2, Chr5_tp1.tp2, Chr6_tp1.tp2, Chr7_tp1.tp2, Chrzw_tp1.tp2#
#adding a chr* column in the dataset

Chr1_tp1.tp2 <- read.table(file.choose(), header = TRUE)
Chr2_tp1.tp2 <- read.table(file.choose(), header = TRUE)
Chr3_tp1.tp2 <- read.table(file.choose(), header = TRUE)
Chr4_tp1.tp2 <- read.table(file.choose(), header = TRUE)
Chr5_tp1.tp2 <- read.table(file.choose(), header = TRUE)
Chr6_tp1.tp2 <- read.table(file.choose(), header = TRUE)
Chr7_tp1.tp2 <- read.table(file.choose(), header = TRUE)
Chrzw_tp1.tp2 <- read.table(file.choose(), header = TRUE)

Chr1_tp1.tp2$CHROM <- c("chr1")
Chr2_tp1.tp2$CHROM <- c("chr2")
Chr3_tp1.tp2$CHROM <- c("chr3")
Chr4_tp1.tp2$CHROM <- c("chr4")
Chr5_tp1.tp2$CHROM <- c("chr5")
Chr6_tp1.tp2$CHROM <- c("chr6")
Chr7_tp1.tp2$CHROM <- c("chr7")
Chrzw_tp1.tp2$CHROM <- c("chrZW")

#adding windows to XPEHH plots#
Chr1_tp1.tp2$start <- Chr1_tp1.tp2$pos
Chr1_tp1.tp2$end <- Chr1_tp1.tp2$start

Chr2_tp1.tp2$start <- Chr2_tp1.tp2$pos
Chr2_tp1.tp2$end <- Chr2_tp1.tp2$start

Chr3_tp1.tp2$start <- Chr3_tp1.tp2$pos
Chr3_tp1.tp2$end <- Chr3_tp1.tp2$start

Chr4_tp1.tp2$start <- Chr4_tp1.tp2$pos
Chr4_tp1.tp2$end <- Chr4_tp1.tp2$start

Chr5_tp1.tp2$start <- Chr5_tp1.tp2$pos
Chr5_tp1.tp2$end <- Chr5_tp1.tp2$start

Chr6_tp1.tp2$start <- Chr6_tp1.tp2$pos
Chr6_tp1.tp2$end <- Chr6_tp1.tp2$start

Chr7_tp1.tp2$start <- Chr7_tp1.tp2$pos
Chr7_tp1.tp2$end <- Chr7_tp1.tp2$start

Chrzw_tp1.tp2$start <- Chrzw_tp1.tp2$pos
Chrzw_tp1.tp2$end <- Chrzw_tp1.tp2$start

XPEHH_tp1.tp2 <- rbind(Chr1_tp1.tp2, Chr2_tp1.tp2, Chr3_tp1.tp2, Chr4_tp1.tp2, Chr5_tp1.tp2, Chr6_tp1.tp2, Chr7_tp1.tp2, Chrzw_tp1.tp2)

bin <- 25000
XPEHH_tp1.tp2 <- XPEHH_tp1.tp2 %>% mutate(window = start %/% bin) %>% group_by(window, CHROM) %>% summarise(mean = mean(normxpehh)) %>% mutate(start = (window*bin)+1, stop = (window+1)*bin)

XPEHH_tp1.tp2_2 <- XPEHH_tp1.tp2[order(XPEHH_tp1.tp2$CHROM, XPEHH_tp1.tp2$start),]
XPEHH_tp1.tp2_2$JT <- seq.int(nrow(XPEHH_tp1.tp2_2))

subset(XPEHH_tp1.tp2_2, XPEHH_tp1.tp2_2$mean < -2 | XPEHH_tp1.tp2_2$mean > 2) -> selected_tp1.tp2
XPEHH_cutoff1_tp1.tp2 <- subset(XPEHH_tp1.tp2_2, mean>2.0)
XPEHH_cutoff2_tp1.tp2 <- subset(XPEHH_tp1.tp2_2, mean< -2.0)

ggplot(data = XPEHH_tp1.tp2_2, aes(JT, mean, color=as.factor(CHROM))) + xlab("Binstart_25kb") + ylab("XPEHH_tp1.tp2") + theme_bw() + geom_rect(aes(xmin=4700,ymin=-5,xmax=4720,ymax=5), fill="grey", color="grey") + geom_point(na.rm = TRUE, size=0.1)

ggplot(data = XPEHH_tp1.tp2_2, aes(JT, mean, color=as.factor(CHROM))) + xlab("Binstart_25kb") + ylab("XPEHH_tp1.tp2") + theme_bw() + geom_rect(aes(xmin=12000,ymin=-6,xmax=12060,ymax=6, size =0.3), fill="grey", color="grey") + geom_point(na.rm = TRUE, size=0.1)

ggplot(data = XPEHH_tp1.tp2_2, aes(JT, mean, color=as.factor(CHROM))) + xlab("Genomic windows (25kb)") + ylab("XPEHH_tp1.tp2") + theme_bw() + geom_point(na.rm = TRUE, size=0.1) + ylim(-5, 5) + geom_hline(yintercept = 2, color="grey", linetype="dashed") + geom_hline(yintercept = -2, color="grey", linetype="dashed") + labs(colour = "Chromosome")

ggplot(data = XPEHH_tp1.tp2_2, aes(JT, mean, color=as.factor(CHROM))) + xlab("Genomic windows (25kb)") + ylab("XPEHH_tp1.tp2") + theme_bw() + geom_hline(yintercept = 2, color="grey", linetype="dashed") + geom_hline(yintercept = -2, color="grey", linetype="dashed") + labs(colour = "Chromosome") + geom_rect(aes(xmin=15023,ymin=-5,xmax=15026,ymax=5), fill="grey", color="grey") + geom_point(na.rm = TRUE, size=0.1)
```

#xpehh for down-sampled
```{r }

c1.t2_std.int <- read.table(file.choose(), header = TRUE)
c2.t2_std.int <- read.table(file.choose(), header = TRUE)
c3.t2_std.int <- read.table(file.choose(), header = TRUE)
c4.t2_std.int <- read.table(file.choose(), header = TRUE)
c5.t2_std.int <- read.table(file.choose(), header = TRUE)
c6.t2_std.int <- read.table(file.choose(), header = TRUE)
c7.t2_std.int <- read.table(file.choose(), header = TRUE)
czw.t2_std.int <- read.table(file.choose(), header = TRUE)

c1.t2_std.int$CHROM <- c("chr1")
c2.t2_std.int$CHROM <- c("chr2")
c3.t2_std.int$CHROM <- c("chr3")
c4.t2_std.int$CHROM <- c("chr4")
c5.t2_std.int$CHROM <- c("chr5")
c6.t2_std.int$CHROM <- c("chr6")
c7.t2_std.int$CHROM <- c("chr7")
czw.t2_std.int$CHROM <- c("chrZW")

c1.t2_std.int$start <- c1.t2_std.int$pos
c1.t2_std.int$end <- c1.t2_std.int$start

c2.t2_std.int$start <- c2.t2_std.int$pos
c2.t2_std.int$end <- c2.t2_std.int$start

c3.t2_std.int$start <- c3.t2_std.int$pos
c3.t2_std.int$end <- c3.t2_std.int$start

c4.t2_std.int$start <- c4.t2_std.int$pos
c4.t2_std.int$end <- c4.t2_std.int$start

c5.t2_std.int$start <- c5.t2_std.int$pos
c5.t2_std.int$end <- c5.t2_std.int$start

c6.t2_std.int$start <- c6.t2_std.int$pos
c6.t2_std.int$end <- c6.t2_std.int$start

c7.t2_std.int$start <- c7.t2_std.int$pos
c7.t2_std.int$end <- c7.t2_std.int$start

czw.t2_std.int$start <- czw.t2_std.int$pos
czw.t2_std.int$end <- czw.t2_std.int$start

xpehh.t2_std.int <- rbind(c1.t2_std.int, c2.t2_std.int, c3.t2_std.int, c4.t2_std.int, c5.t2_std.int, c6.t2_std.int, c7.t2_std.int, czw.t2_std.int)

bin <- 25000
Xpehh.t2_std.int <- xpehh.t2_std.int %>% mutate(window = start %/% bin) %>% group_by(window, CHROM) %>% summarise(mean = mean(normxpehh)) %>% mutate(start = (window*bin)+1, stop = (window+1)*bin)

Xpehh.t2_std.int <- Xpehh.t2_std.int[order(Xpehh.t2_std.int$CHROM, Xpehh.t2_std.int$start),]
Xpehh.t2_std.int$jv <- seq.int(nrow(Xpehh.t2_std.int))

subset(Xpehh.t2_std.int, Xpehh.t2_std.int$mean < -2 | Xpehh.t2_std.int$mean > 2) -> crit.t2_std.int

ggplot(data = Xpehh.t2_std.int, aes(jv, mean, color=as.factor(CHROM))) + xlab("Genomic windows (25kb)") + ylab("XP-EHH.t2_std.int") + theme_bw() + geom_point(na.rm = TRUE, size=0.1) + ylim(-5, 5) + geom_hline(yintercept = 2, color="grey", linetype="dashed") + geom_hline(yintercept = -2, color="grey", linetype="dashed") + labs(colour = "Chromosome") + ggtitle("XP-EHH for down-sampled post-treatment_std.int") + geom_rect(aes(xmin=10149,ymin=-5,xmax=10176,ymax=5), fill="grey", color="grey") + geom_point(na.rm = TRUE, size=0.1)

```

#Plotting nucleotide diversity#
```{r   }
nd_std <- read.delim(file.choose())
nd_int <- read.delim(file.choose())
nd_pre <- read.delim(file.choose())
nd_post <- read.delim(file.choose())
pre.std <- read.delim(file.choose())
pre.int <- read.delim(file.choose())
post.std <- read.delim(file.choose())
post.int <- read.delim(file.choose())

pre51 <- read.delim(file.choose())
post51 <- read.delim(file.choose())
pre_std51 <- read.delim(file.choose())
pre_int51 <- read.delim(file.choose())
post_std51 <- read.delim(file.choose())
post_int51 <- read.delim(file.choose())

#*******************************************************#pre51
mean_pi <- mean(pre51$PI)
median_pi <- median(pre51$PI)
bstrap_means <- c()
bstrap_medians <- c()
for (i in 1:100) { 
 bstrap_medians <- c(bstrap_medians,median(sample(pre51$PI,size=length(pre51$PI),replace=TRUE)))
 bstrap_means <- c(bstrap_means,mean(sample(pre51$PI,size=length(pre51$PI),replace=TRUE)))
}
#these are symmetric 99% bootstrap confidence intervals for your median and mean, respectively
quantile(bstrap_medians,c(0.005,0.995))
quantile(bstrap_means,c(0.005,0.995))
#these are symmetric 95% bootstrap confidence intervals for your median and mean
quantile(bstrap_medians,c(0.025,0.975))
quantile(bstrap_means,c(0.025,0.975))
#*************************************************************#post51
mean_pi <- mean(post51$PI)
median_pi <- median(post51$PI)
bstrap_means <- c()
bstrap_medians <- c()
for (i in 1:100) { 
 bstrap_medians <- c(bstrap_medians,median(sample(post51$PI,size=length(post51$PI),replace=TRUE)))
 bstrap_means <- c(bstrap_means,mean(sample(post51$PI,size=length(post51$PI),replace=TRUE)))
}
#these are symmetric 99% bootstrap confidence intervals for your median and mean, respectively
quantile(bstrap_medians,c(0.005,0.995))
quantile(bstrap_means,c(0.005,0.995))
#these are symmetric 95% bootstrap confidence intervals for your median and mean
quantile(bstrap_medians,c(0.025,0.975))
quantile(bstrap_means,c(0.025,0.975))
#***************************************************************#pre_std51
mean_pi <- mean(pre_std51$PI)
median_pi <- median(pre_std51$PI)
bstrap_means <- c()
bstrap_medians <- c()
for (i in 1:100) { 
 bstrap_medians <- c(bstrap_medians,median(sample(pre_std51$PI,size=length(pre_std51$PI),replace=TRUE)))
 bstrap_means <- c(bstrap_means,mean(sample(pre_std51$PI,size=length(pre_std51$PI),replace=TRUE)))
}
#these are symmetric 99% bootstrap confidence intervals for your median and mean, respectively
quantile(bstrap_medians,c(0.005,0.995))
quantile(bstrap_means,c(0.005,0.995))
#these are symmetric 95% bootstrap confidence intervals for your median and mean
quantile(bstrap_medians,c(0.025,0.975))
quantile(bstrap_means,c(0.025,0.975))
#********************************************************#pre_int51
mean_pi <- mean(pre_int51$PI)
median_pi <- median(pre_int51$PI)
bstrap_means <- c()
bstrap_medians <- c()
for (i in 1:100) { 
 bstrap_medians <- c(bstrap_medians,median(sample(pre_int51$PI,size=length(pre_int51$PI),replace=TRUE)))
 bstrap_means <- c(bstrap_means,mean(sample(pre_int51$PI,size=length(pre_int51$PI),replace=TRUE)))
}
#these are symmetric 99% bootstrap confidence intervals for your median and mean, respectively
quantile(bstrap_medians,c(0.005,0.995))
quantile(bstrap_means,c(0.005,0.995))
#these are symmetric 95% bootstrap confidence intervals for your median and mean
quantile(bstrap_medians,c(0.025,0.975))
quantile(bstrap_means,c(0.025,0.975))
#****************************************************#post_std51
mean_pi <- mean(post_std51$PI)
median_pi <- median(post_std51$PI)
bstrap_means <- c()
bstrap_medians <- c()
for (i in 1:100) { 
 bstrap_medians <- c(bstrap_medians,median(sample(post_std51$PI,size=length(post_std51$PI),replace=TRUE)))
 bstrap_means <- c(bstrap_means,mean(sample(post_std51$PI,size=length(post_std51$PI),replace=TRUE)))
}
#these are symmetric 99% bootstrap confidence intervals for your median and mean, respectively
quantile(bstrap_medians,c(0.005,0.995))
quantile(bstrap_means,c(0.005,0.995))
#these are symmetric 95% bootstrap confidence intervals for your median and mean
quantile(bstrap_medians,c(0.025,0.975))
quantile(bstrap_means,c(0.025,0.975))
#**********************************************************#post_int51
mean_pi <- mean(post_int51$PI)
median_pi <- median(post_int51$PI)
bstrap_means <- c()
bstrap_medians <- c()
for (i in 1:100) { 
 bstrap_medians <- c(bstrap_medians,median(sample(post_int51$PI,size=length(post_int51$PI),replace=TRUE)))
 bstrap_means <- c(bstrap_means,mean(sample(post_int51$PI,size=length(post_int51$PI),replace=TRUE)))
}
#these are symmetric 99% bootstrap confidence intervals for your median and mean, respectively
quantile(bstrap_medians,c(0.005,0.995))
quantile(bstrap_means,c(0.005,0.995))
#these are symmetric 95% bootstrap confidence intervals for your median and mean
quantile(bstrap_medians,c(0.025,0.975))
quantile(bstrap_means,c(0.025,0.975))
#*************************************************************

nd_std_nohap <- subset(nd_std, CHROM=="SM_V7_4_5" | CHROM=="SM_V7_1_1" | CHROM=="SM_V7_2_4" | CHROM=="SM_V7_3_3" | CHROM=="SM_V7_5_6" | CHROM=="SM_V7_6_7" | CHROM=="SM_V7_7_8" | CHROM=="SM_V7_ZW_2")

ggplot(data = nd_std_nohap, aes(1:nrow(nd_std_nohap), PI, color=as.factor(CHROM))) + geom_point(size=0.1) + theme_bw() + xlab("Position along the genome") + ylab("Nulceotide diversity ()") + ggtitle("Nulceotide diversity for the standard arm") + theme(plot.title = element_text(hjust = 0.5))

# int_nd#
nd_int <- read.delim(file.choose())

nd_int_nohap <- subset(nd_int, CHROM=="SM_V7_4_5" | CHROM=="SM_V7_1_1" | CHROM=="SM_V7_2_4" | CHROM=="SM_V7_3_3" | CHROM=="SM_V7_5_6" | CHROM=="SM_V7_6_7" | CHROM=="SM_V7_7_8" | CHROM=="SM_V7_ZW_2")

ggplot(data = nd_int_nohap, aes(1:nrow(nd_int_nohap), PI, color=as.factor(CHROM))) + geom_point(size=0.1) + theme_bw() + xlab("Position along the genome") + ylab("Nulceotide diversity ()") + ggtitle("Nulceotide diversity for the intensive arm") + theme(plot.title = element_text(hjust = 0.5))

mean(nd_int_nohap$PI)

#pre_nd#
nd_pre <- read.delim(file.choose())

nd_pre_nohap <- subset(nd_pre, CHROM=="SM_V7_4_5" | CHROM=="SM_V7_1_1" | CHROM=="SM_V7_2_4" | CHROM=="SM_V7_3_3" | CHROM=="SM_V7_5_6" | CHROM=="SM_V7_6_7" | CHROM=="SM_V7_7_8" | CHROM=="SM_V7_ZW_2")

ggplot(data = nd_pre_nohap, aes(1:nrow(nd_pre_nohap), PI, color=as.factor(CHROM))) + geom_point(size=0.1) + theme_bw() + xlab("Position_binstart") + ylab("Nulceotide diversity ()") + ggtitle("Nulceotide diversity for the pre-treatment arm") + theme(plot.title = element_text(hjust = 0.5))

mean(nd_pre_nohap$PI)

#post_nd#
nd_post <- read.delim(file.choose())
nd_post_nohap <- subset(nd_post, CHROM=="SM_V7_4_5" | CHROM=="SM_V7_1_1" | CHROM=="SM_V7_2_4" | CHROM=="SM_V7_3_3" | CHROM=="SM_V7_5_6" | CHROM=="SM_V7_6_7" | CHROM=="SM_V7_7_8" | CHROM=="SM_V7_ZW_2")

ggplot(data = nd_post_nohap, aes(1:nrow(nd_post_nohap), PI, color=as.factor(CHROM))) + geom_point(size=0.1) + theme_bw() + xlab("Position along the genome") + ylab("Nulceotide diversity ()") + ggtitle("Nulceotide diversity for the post-treatment arm") + theme(plot.title = element_text(hjust = 0.5))

mean(nd_post_nohap$PI)
                    
#koome_nd#
nd_koome <- read.delim(file.choose())

nd_koome_nohap <- subset(nd_koome, CHROM=="SM_V7_4_5" | CHROM=="SM_V7_1_1" | CHROM=="SM_V7_2_4" | CHROM=="SM_V7_3_3" | CHROM=="SM_V7_5_6" | CHROM=="SM_V7_6_7" | CHROM=="SM_V7_7_8" | CHROM=="SM_V7_ZW_2")

ggplot(data = nd_koome_nohap, aes(1:nrow(nd_koome_nohap), PI, color=as.factor(CHROM))) + geom_point(size=0.1) + theme_bw() + xlab("Position_binstart") + ylab("Nulceotide diversity ()") + ggtitle("Nulceotide diversity for Koome island") + theme(plot.title = element_text(hjust = 0.5))

mean(nd_koome_nohap$PI)

#damba_nd#
nd_damba <- read.delim(file.choose())

nd_damba_nohap <- subset(nd_damba, CHROM=="SM_V7_4_5" | CHROM=="SM_V7_1_1" | CHROM=="SM_V7_2_4" | CHROM=="SM_V7_3_3" | CHROM=="SM_V7_5_6" | CHROM=="SM_V7_6_7" | CHROM=="SM_V7_7_8" | CHROM=="SM_V7_ZW_2")

ggplot(data = nd_damba_nohap, aes(1:nrow(nd_damba_nohap), PI, color=as.factor(CHROM))) + geom_point(size=0.1) + theme_bw() + xlab("Position_binstart") + ylab("Nulceotide diversity ()") + ggtitle("Nulceotide diversity for Damba island") + theme(plot.title = element_text(hjust = 0.5))

mean(nd_damba_nohap$PI)

# mean nucleotide diversity#
mean_nd <- read.csv(file.choose())

ggplot(data = mean_nd, aes(x=Group, y=Mean, group=1)) + theme_bw() + geom_point() + geom_line(color="purple") + ggtitle("Mean nulceotide diversity") + theme(plot.title = element_text(hjust = 0.5)) + xlab("") + ylab("Mean ()") + ggpubr::rotate_x_text()

ND <- read.csv(file.choose())
boxplot(ND, na.rm=T)
ND_2 <- (melt(ND))

# *** use melt command from reshape2 to transform data from long to wide format and then plot it.
ggplot(ND_2) + geom_violin(aes(x=variable, y=value))
ggplot(ND_2) + geom_boxplot(aes(x=variable, y=value))
ggplot(ND_2) + geom_boxplot(aes(x=variable, y=-log10(value)))

#*** ND per site ***#
ND_site_std <- read.delim(file.choose())
ND_site_int <- read.delim(file.choose())
ND_site_tp1 <- read.delim(file.choose())
ND_site_tp2 <- read.delim(file.choose())
ND_site_koome <- read.delim(file.choose())
ND_site_damba <- read.delim(file.choose())

ND_2 <-  ND_site_std$PI
ND_2$Intensive <- ND_site_int$PI
ND_2 <-  c(ND_site_std$PI)
names(ND_2)[3] <- "Standard"
ND_2$Standard <- ND_site_std$PI

mean_2 <- read.csv(file.choose())

ggplot(data = mean_2, aes(grp, mN)) + geom_point() + geom_boxplot() + theme_bw() + ylab("Mean ") + ggtitle("Mean genome-wide nucleotide diversity") + theme(plot.title = element_text(hjust = 0.5)) 

#nucleotide diversity from all groups combined together#
Nucleotide_all <- read.delim(file.choose(), header=FALSE)

ND_all <- subset(Nucleotide_all, V1=="SM_V7_4_5" | V1=="SM_V7_1_1" | V1=="SM_V7_2_4" | V1=="SM_V7_3_3" | V1=="SM_V7_5_6" | V1=="SM_V7_6_7" | V1=="SM_V7_7_8" | V1=="SM_V7_ZW_2")

colnames(ND_all)[colnames(ND_all)=="V1"] <- "CHROM"
colnames(ND_all)[colnames(ND_all)=="V2"] <- "POS"
colnames(ND_all)[colnames(ND_all)=="V3"] <- "pi"
colnames(ND_all)[colnames(ND_all)=="V4"] <- "grp"

ggplot(data = ND_all, aes(x=CHROM, y=pi, color=as.factor(CHROM))) + geom_point() + theme_bw() + geom_boxplot() + ylab("Nucleotide diversity ()")

ggplot(data = ND_all, aes(x=grp, y=pi, color=as.factor(grp))) + geom_point() + theme_bw() + geom_boxplot() + ylab("Nucleotide diversity ()")

ggplot(data = ND_all, aes(1:nrow(ND_all), pi, color=as.factor(grp))) + geom_point(size=0.1) + theme_bw() 
ggplot(data = ND_all, aes(1:nrow(ND_all), V3, color=as.factor(V4))) + theme_bw() + geom_point()

Zingoola.pi <- read.delim(file.choose(), header = T)
Busi.pi <- read.delim(file.choose())
Kakeeka.pi <- read.delim(file.choose())
Kachanga.pi <- read.delim(file.choose())
Katooke.pi <- read.delim(file.choose())
Kisu.pi <- read.delim(file.choose())
lugumba.pi <- read.delim(file.choose())
Kitosi.pi <- read.delim(file.choose())

Zgoola.pi <- subset(Zingoola.pi, CHROM=="SM_V7_1" | CHROM=="SM_V7_2" | CHROM=="SM_V7_3" |CHROM=="SM_V7_4" 
                    | CHROM=="SM_V7_5" | CHROM=="SM_V7_6" | CHROM=="SM_V7_7" | CHROM=="SM_V7_ZW")
Bsi.pi <- subset(Busi.pi, CHROM=="SM_V7_1" | CHROM=="SM_V7_2" | CHROM=="SM_V7_3" |CHROM=="SM_V7_4" 
                    | CHROM=="SM_V7_5" | CHROM=="SM_V7_6" | CHROM=="SM_V7_7" | CHROM=="SM_V7_ZW")
Keeka.pi <- subset(Kakeeka.pi, CHROM=="SM_V7_1" | CHROM=="SM_V7_2" | CHROM=="SM_V7_3" |CHROM=="SM_V7_4" 
                    | CHROM=="SM_V7_5" | CHROM=="SM_V7_6" | CHROM=="SM_V7_7" | CHROM=="SM_V7_ZW")
Kchanga.pi <- subset(Kachanga.pi, CHROM=="SM_V7_1" | CHROM=="SM_V7_2" | CHROM=="SM_V7_3" |CHROM=="SM_V7_4" 
                    | CHROM=="SM_V7_5" | CHROM=="SM_V7_6" | CHROM=="SM_V7_7" | CHROM=="SM_V7_ZW")
Ktooke.pi <- subset(Katooke.pi, CHROM=="SM_V7_1" | CHROM=="SM_V7_2" | CHROM=="SM_V7_3" |CHROM=="SM_V7_4" 
                    | CHROM=="SM_V7_5" | CHROM=="SM_V7_6" | CHROM=="SM_V7_7" | CHROM=="SM_V7_ZW")
Ksu.pi <- subset(Kisu.pi, CHROM=="SM_V7_1" | CHROM=="SM_V7_2" | CHROM=="SM_V7_3" |CHROM=="SM_V7_4" 
                    | CHROM=="SM_V7_5" | CHROM=="SM_V7_6" | CHROM=="SM_V7_7" | CHROM=="SM_V7_ZW")
Lgumba.pi <- subset(lugumba.pi, CHROM=="SM_V7_1" | CHROM=="SM_V7_2" | CHROM=="SM_V7_3" |CHROM=="SM_V7_4" 
                    | CHROM=="SM_V7_5" | CHROM=="SM_V7_6" | CHROM=="SM_V7_7" | CHROM=="SM_V7_ZW")
Ktosi.pi <- subset(Kitosi.pi, CHROM=="SM_V7_1" | CHROM=="SM_V7_2" | CHROM=="SM_V7_3" |CHROM=="SM_V7_4" 
                    | CHROM=="SM_V7_5" | CHROM=="SM_V7_6" | CHROM=="SM_V7_7" | CHROM=="SM_V7_ZW")
      
ndVillages <- read.delim(file.choose())
ggplot(ndVillages, aes(Village, PI, color = as.factor(Island))) +theme_bw() + geom_boxplot() + scale_color_discrete(name = "Island") +ggtitle("Per village average nucleotide diversity")

nd1 <- Zgoola.pi %>% select(matches("PI"))
colnames(nd1) <- "Zingoola"

nd2 <- Bsi.pi %>% select(matches("PI"))
colnames(nd2) <- "Busi"

nd3 <- Keeka.pi %>% select(matches("PI"))
colnames(nd3) <- "Kakeeka"

nd4 <- Kchanga.pi %>% select(matches("PI"))
colnames(nd4) <- "Kachanga"

nd5 <- Ktooke.pi %>% select(matches("PI"))
colnames(nd5) <- "Katooke"

nd6 <- Ksu.pi %>% select(matches("PI"))
colnames(nd6) <- "Kisu"

nd7 <- Lgumba.pi %>% select(matches("PI"))
colnames(nd7) <- "Lugumba"

nd8 <- Ktosi.pi %>% select(matches("PI"))
colnames(nd8) <- "Kitosi"

set.seed(1)
cbindPad <- function(...){
args <- list(...)
n <- sapply(args,nrow)
mx <- max(n)
pad <- function(x, mx){
    if (nrow(x) < mx){
        nms <- colnames(x)
        padTemp <- matrix(NA, mx - nrow(x), ncol(x))
        colnames(padTemp) <- nms
        if (ncol(x)==0) {
          return(padTemp)
        } else {
        return(rbind(x,padTemp))
          }
    }
    else{
        return(x)
    }
}
rs <- lapply(args,pad,mx)
return(do.call(cbind,rs))
}

Vnd <- cbindPad(nd1, nd2, nd3, nd4, nd5, nd6, nd7, nd8)
```

```{r }
cutoff <- XPEHH_std.int_2 %>% summarize(lower = quantile(XPEHH_std.int_2$mean, probs = 0.005), upper = quantile(XPEHH_std.int_2$mean, probs = 0.997))

ggplot(XPEHH_std.int_2, aes(x = XPEHH_std.int_2$mean)) + geom_density() + geom_vline(data = cutoff, aes(xintercept = lower)) + geom_vline(data = cutoff, aes(xintercept = upper)) + theme_bw()
```
```{r }
#Fixing the metadata# #tsv file exported from Google sheets on 19/8/2020
data <- read.csv(file.choose())

#do name and number match up?
table(data$Village.name..Vname.,data$Village.number..Vno.)

#all in same country and district
unique(data$Country)
unique(data$District)

#each village has a single treatment group
table(data$Village.name..Vname.,data$Treatment)

#is each village on a single island
table(data$Island,data$Village.name..Vname.)

#all sample ID and sanger sample ID are unique
length(unique(data$SampleID))
length(unique(data$Sanger_Sample_ID))

#96 possible infrapop IDs - but that is ok.
#length(unique(data$Infrapop_ID))

#timespan
time.between <- function(x) {
max(dmy(x)) - min(dmy(x))}

#distribution of sampling dates for each village, and for each village by sampling point
for (i in unique(data$Village.name..Vname.)) {
print(i);
t <- time.between(data$Collection.date[data$VillageName..Vname. == i]);
print(as.double(t,units="days")); for (j in unique(data$TimePoint)) { print(c(i,j))
    t1 <- time.between(data$Collection.date[data$VillageName..Vname. == i & data$TimePoint == j]);
    print(as.double(t1,units="days"));
}}

#Zingoola and Katooke sampling time point 1 seem very wide.
#which points are weird - are there outliers?
#would plot this if many points

data$Collection.date[data$Village.name..Vname. == "Zingoola" & data$Time.point..1.enrolment.pre.treatment..2.follow.up.post.treatemnt. == 1]
data$Collection.date[data$Village.name..Vname. == "Katooke" & data$Time.point..1.enrolment.pre.treatment..2.follow.up.post.treatemnt. == 1]

```


```{r }
pdata <- read.csv(file.choose())

md.96 <- pdata %>% distinct(Infrapop_ID, .keep_all = TRUE)
Tp1.uniq <- md.96[which(md.96$Tp=="1"), ]
Tp2.uniq <- md.96[which(md.96$Tp=="2"), ]

Tp1.uniq.int <- md.uniq[which(md.uniq$Time.point=="1" & md.uniq$Treatment=="intensive"), ]
Tp1.uniq.std <- md.uniq[which(md.uniq$Time.point=="1" & md.uniq$Treatment=="Standard"), ]

Tp2.uniq <- md.uniq[which(md.uniq$Time.point=="2"), ]
Tp2.uniq.std <- md.uniq[which(md.uniq$Time.point=="2" & md.uniq$Treatment=="Standard"), ]
Tp2.uniq.int <- md.uniq[which(md.uniq$Time.point=="2" & md.uniq$Treatment=="Intensive"), ]

count(Tp2.uniq)
count(Tp1.uniq)
count(Tp1.uniq.int)
count(Tp1.uniq.std)
count(Tp2.uniq.std)
count(Tp2.uniq.int)

Tp2 <- pdata[which(pdata$Tp=="2"), ] #51
Tp1 <- pdata[which(pdata$Tp=="1"), ] #123
Tp1.uniq <- Tp1 %>% distinct(Infrapop_ID, .keep_all = TRUE) #79
Tp2.uniq <- Tp2 %>% distinct(Infrapop_ID, .keep_all = TRUE)

write.csv(Tp2, file = "Tp2.uniq.csv")
write.csv(Tp1.uniq, file = "Tp1_79.csv")

xx <- pdata %>% filter(Treatment=="Intensive", Tp == 2) # quite useful

#filtering unique eggs data by infrapopID
eggs <- read.csv(file.choose())
eggsUniq <- eggs %>% distinct(infrapop_id, .keep_all = TRUE)
write.csv(eggsUniq, file = "Eggs_88.csv")
```

```{r }

sib <- read.delim(file.choose(), header = TRUE)
related <- sib %>% filter(sib$Kinship>0)
Full <- sib %>% filter(sib$Kinship>0.25)
Monozygotic <- sib %>% filter(sib$Kinship>0.5)

Related <- read.delim(file.choose(), header = TRUE)

ggplot(data = Related, aes(x=IBS0, y=Kinship)) + geom_point() + theme_bw() + xlab("Proportion of Zero IBS") + ylab("Estimated Kinship Coefficient") + ggtitle("Between-Family Relationship") + theme(plot.title = element_text(hjust = 0.5))

```


```{r regions_genes under selection}
## load libraries
library(tidyverse)
library(knitr)
library(readxl)

setwd("/Users/tushabejohnvianney/PopGen_paper")

regions_genes <- readxl::read_xlsx("Regions_genes_under_selection.xlsx")
regions_int <- regions_genes %>% filter(Group=="Intensive")
regions_post <- regions_genes %>% filter(Group=="Post.treatment")




```


























